Crowdy: Social Crowd Visualization

### 2011-03-01 docs/crowdy_gui.tex
wraped lines in crowdy_gui.tex to 80 characters
merged related work and reference section

\numberofauthors{1} 
\author{\alignauthor Jeffrey McGee, Zhiyuan Cheng, Chiao-Fang Hsu, Pratheek Kumar Akireddy \\
\affaddr{Department of Computer Science and Engineering, Texas A\&M University} \\ \affaddr{ College Station, TX 77845 USA} \\
\email{jeffamcgee@gmail.com, chengzhy@gmail.com, drakihsu@cse.tamu.edu, pka293@cse.tamu.edu}
}

@@

\section{Related Work}

>>>>

\numberofauthors{1} 
\author{
    \alignauthor Jeffrey McGee, Zhiyuan Cheng, Chiao-Fang Hsu, Pratheek
    Kumar Akireddy \\
    \affaddr{Department of Computer Science and Engineering, Texas A\&M
    University} \\
    \affaddr{ College Station, TX 77845 USA} \\
    \email{jeffamcgee@gmail.com, chengzhy@gmail.com, drakihsu@cse.tamu.edu,
    pka293@cse.tamu.edu}
}

@@

\section{Related Work}
Twitter is a microblogging platform which is fast gaining popularity
among broad sections of society and has a global outreach spreading from
developed, urban nations the likes of the United States where it has a high
adoption rate\cite{akshayjava2009we}, to developing countries in parts of Asia
and South America.

Along with working on understanding microblogging usage and
communities\cite{java2007we}, the main author - Akshay Java was one of the
first few who dealt with the measurement of the usage and nature of communities
in microblogging. In his latter study\cite{java2008mining}, he presented his
observations of the microblogging phenomena and user intentions by studying the
content, topological and geographical properties of such communities. He found
that microblogging provides users with a more immediate form of communication
to talk about their daily activities and to seek or share information.

When it comes to visualization of the social crowd, a tool which in some ways
shows similar objectives as us and stands out among the rest is
Vizster\cite{heer2005vizster}. It is a visualization system for playful
end-user exploration and navigation of large-scale online social networks. The
design builds upon familiar node- link network layouts to contribute techniques
for exploring connectivity in large graph structures, supporting visual search
and analysis, and automatically identifying and visualizing community
structures. The system facilitates a better discovery of people, connections,
and communities to promote increased awareness of community structure and
information exposure, while maintaining a fun and socially engaged online
space. The creators of the tool were interested in crafting techniques for the
situated exploration and visual analysis of large graph structures by a
specific end-user population.

Another related study was on how web-based retrieval from twitter can be used
as knowledge base\cite{cheong2009integrating} which shows that the
visualization system we try to attempt can be helpful. Marc Cheong et al. in
this study tried to analyze demographics of the authors of Twitter messages and
attempt to map a Twitter trend into what's going on in the real world. Their
findings reveal a pattern behind trends on Twitter, and trying to evolve
through visualization methods.  Their findings also enable us to understand the
underlying characteristics behind the ``trend setters'', providing us a new
perspective on the contributors of a trend.

Identifying highly dynamic ad-hoc collections of users what we refer to as
crowds in massive social messaging systems like Twitter and Facebook is
important\cite{kamath2010identifying}. K. Y. Kamath et al. in the study have a
salient feature of the proposed approach as an efficient locality-based
clustering approach for identifying crowds of users in near real-time compared
to more heavyweight static clustering algorithm. The study consisted of 711,612
users and 61.3 million messages, which show how the proposed approach can
efficiently and effectively identify Twitter-based crowds.

In the other study based on the previous one, K. Y. Kamath et
al\cite{kamath2011transient}, they add another salient feature - a novel crowd
tracking and evolution approach for linking crowds across time periods. Unlike
the more static and long-lived group-based membership offered on many social
networks their goal is to support the discovery of organic and highly-temporal
group affiliation, which they refer to as ``transient crowds''. A transient
crowd according to them is a potentially short-lived ad-hoc collection of users
bound together by some common thread – which can be communication-based,
location-based or interest based. We are inspired by this idea of formation and
detection of crowds. We try to implement detection of crowd in “crowdy” in a
similar fashion.
